Ladies' figure skating in the 2002 Winter Olympics

### 2025-11-25 inst/skating.Rmd
soft link for hyper2.bib
typo

---
title: "Ladies' figure skating in the 2002 Winter Olympics"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib  # copy vignettes/hyper2.bib to inst/
---

@@

To cite the `hyper2` package in publications, please use
@hankin2017_rmd).  This document analyses Bradley-Terry strengths of
the competitors in the Ladies' Figure Skating at the 2002 Winter
Olympics.  In the package, dataframe `skating_table` is copied from
Lock and Lock (see skating.Rd for more details).  It also creates file
`data/skating.rda` which contains R objects `skating`,
`skating_table`, and `skating_maxp`.

>>>>

---
title: "Ladies' figure skating in the 2002 Winter Olympics"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.  This document analyses Bradley-Terry strengths of
the competitors in the Ladies' Figure Skating at the 2002 Winter
Olympics.  In the package, dataframe `skating_table` is copied from
Lock and Lock (see skating.Rd for more details).  It also creates file
`data/skating.rda` which contains R objects `skating`,
`skating_table`, and `skating_maxp`.
